### 2013-03-28 doc/sosp13/tasks.tex
Update stuff about how we specify tasks (with lambdas).

\paragraph{Tasks} Each task is represented by a 64-bit function pointer and
three 64-bit arguments. We use three arguments because tasks are often
generated via a parallel loop decomposition, in which each task needs three
kinds of data:

\begin{itemize}
\item {\it private argument}, often a loop index;

\item {\it shared argument}, typically data shared amongst a group of
tasks, or the number of loop iterations to be performed by this task;

\item {\it synchronization argument}, often used to determine when all
tasks that are part of a loop have finished, in the form of a global pointer
to a synchronization object allocated at the core that spawned a group of
tasks.
\end{itemize}

While these are the most common uses of the three task arguments, they are
treated as arbitrary 64-bit values in the runtime, and can be used for any
purpose.

\paragraph{Workers} Workers execute application and system (e.g.,
communication) tasks. A worker is simply a collection of status bits and a
stack, allocated at a particular core. When a task is ready to be executed it
is assigned to a worker. Once a task is mapped to a worker it stays with that
worker until it completes.

>>>>

\paragraph{Tasks} 
Tasks are specified with a ``functor'' object that holds both code to execute and initial state. The functor can be specified with a function pointer and explicit arguments, a C++ struct that overloads the parentheses operator, or a C++11 lambda. These objects, typically very small (on the order of 64 bytes), hold read-only values such as an iteration index and pointers to common data or synchronization objects. These task functors can be serialized and transported around the system, and eventually executed by a Worker, as described next.

\paragraph{Workers} Workers execute application and system (e.g.,
communication) tasks. A worker is simply a collection of status bits and a
stack, allocated at a particular core. When a task is ready to be executed it
is assigned to a worker, which executes the task functor on its own stack. 
Once a task is mapped to a worker it stays with that worker until it finishes.
